Really Hard Instances for the Subgraph Isomorphism Problem

### 2015-09-14 paper/paper.tex
More plotting

\subsection{Varying Densities}

\subsection{Varying Sizes}

@@

@@

\begin{figure*}[tb]
    \input{gen-graph-sat.tex}
    \caption{Behaviour of other solvers on the induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern density and the y-axis is the target
        density, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. On the second row, we show the
        number of search nodes used by the Glasgow algorithm, and on the third row, the number of
        conflicts recorded by the Glucose SAT solver: the dark regions indicate ``really hard''
        instances. These results show that instances which are hard for the Glasgow algorithm tend
        to be hard using other solvers too, but do not otherwise allow comparisons between solver
        performances.}
\end{figure*}

>>>>

\begin{figure*}[p]
    \input{gen-graph-non-induced.tex}
    \setlength{\abovecaptionskip}{-3em}
    \caption{Behaviour of algorithms on the non-induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern density and the y-axis is the target
        density, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. On the second row, we show the
        number of search nodes used by the Glasgow algorithm, and on the third row, the number of
        search nodes used by the VF2 algorithm: the dark regions indicate ``really hard''
        instances.}
\end{figure*}

@@

\begin{figure*}[p]
    \input{gen-graph-induced.tex}
    \setlength{\abovecaptionskip}{-3em}
    \caption{Behaviour of algorithms on the induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern density and the y-axis is the target
        density, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. On the second row, we show the
        number of search nodes used by the Glasgow algorithm, and on the third row, the number of
        search nodes used by the VF2 algorithm: the dark regions indicate ``really hard''
        instances.}
\end{figure*}

@@

\begin{figure*}[tb]
    \input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-3em}
    \caption{Behaviour of other solvers on the induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern density and the y-axis is the target
        density, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. On the second row, we show the
        number of search nodes used by the Glasgow algorithm, and on the third row, the number of
        decisions made by the Glucose SAT solver: the dark regions indicate ``really hard''
        instances. These results show that instances which are hard for the Glasgow algorithm tend
        to be hard using other solvers too.}
\end{figure*}
